---
title: "p8105_hw6_yh3430"
author: "Yu He"
date: "11/28/2021"
output: github_document
---
Load libraries

```{r}
library(tidyverse)
library(viridis)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

## problem 1 model 1

import and clean data 

```{r}
birthweight_data =
  read_csv("birthweight.csv") %>% 
  mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    malform = factor(malform),
    mrace = factor(mrace)
  )
```

Let's check if there is missing values

```{r}
sum(is.na(birthweight_data))
```

Let's make a plot to see some data

```{r}
birthweight_data %>% 
  ggplot(aes(x = fincome, y = bwt)) +
  geom_point()

birthweight_data %>% 
  ggplot(aes(x = ppbmi, y = bwt)) +
  geom_point()
```

Let's fit a linear model

```{r}
fit_df = lm(bwt ~ fincome + ppbmi, data = birthweight_data)
summary(fit_df)
```

Diagnostics

```{r}
add_residuals(birthweight_data, fit_df) %>% 
  ggplot(aes(x = fincome, y = resid)) +
  geom_point() +
  geom_point(aes(x = ppbmi, color = "red"))

add_residuals(birthweight_data, fit_df) %>% 
  ggplot(aes(x = resid)) +
  geom_density()
  
```

## problem 1 model 2 and 3

model 2 using birth length and gestational age in weeks at predictors

```{r}
fit_df2 = lm(bwt ~ blength + gaweeks, data = birthweight_data)
summary(fit_df2)
```

model 3 using head circumference, length, sex and all interactions

```{r}
fit_df3 = lm(bwt ~ babysex + bhead + blength + babysex * bhead + babysex * blength + bhead * blength + babysex * bhead * blength, data = birthweight_data)
summary(fit_df3)
```

## problem 1 use CV to compare models

```{r}
cv_df_p1 = 
  crossv_mc(birthweight_data, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

fit models and extract RMSE

```{r}
cv_df1_RMSE =
  cv_df_p1 %>% 
  mutate(
    mod_df1 = map(.x = train, ~lm(bwt ~ fincome + ppbmi, data = .x)),
    mod_df2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_df3 = map(.x = train, ~lm(bwt ~ babysex + bhead + blength + babysex * bhead + babysex * blength + bhead * blength + babysex * bhead * blength, data = .x))
  ) %>% 
  mutate(
    rmse_df1 = map2_dbl(.x = mod_df1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_df2 = map2_dbl(.x = mod_df2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_df3 = map2_dbl(.x = mod_df3, .y = test, ~rmse(model = .x, data = .y))
  )
```

RMSE distribution

```{r}
cv_df1_RMSE %>% 
  select(.id, starts_with("rmse")) %>% 
    pivot_longer(
    rmse_df1:rmse_df3,
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_boxplot()
  
```
































