---
title: "p8105_hw6_yh3430"
author: "Yu He"
date: "11/28/2021"
output: github_document
---
Load libraries

```{r}
library(tidyverse)
library(viridis)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

## problem 1 model 1

import and clean data 

```{r}
birthweight_data =
  read_csv("birthweight.csv") %>% 
  mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    malform = factor(malform),
    mrace = factor(mrace)
  )
```

Let's check if there is missing values

```{r}
sum(is.na(birthweight_data))
```

Let's make a plot to see some data. Based on my knowledge, I first select the family monthly income, average number of cigarettes smoked per day during pregnancy, and mother's pre-pregnancy BMI as the predictor. From the figure below, the distribution of fincome and smoken looks good, but the distribution of ppbmi gathered relatively together. I think it is ok to start a simple linear model based on these three factors.

```{r}
birthweight_data %>% 
  ggplot(aes(x = fincome, y = bwt)) +
  geom_point()

birthweight_data %>% 
  ggplot(aes(x = smoken, y = bwt)) +
  geom_point()

birthweight_data %>% 
  ggplot(aes(x = ppbmi, y = bwt)) +
  geom_point()
```

Let's fit a linear model

```{r}
fit_df = lm(bwt ~ fincome + smoken + ppbmi, data = birthweight_data)
summary(fit_df)
```

Diagnostics

```{r}
add_residuals(birthweight_data, fit_df) %>% 
  ggplot(aes(x = fincome, y = resid)) +
  geom_point() +
  geom_point(aes(x = ppbmi, color = "red")) +
  geom_point(aes(x = smoken, color = "blue"))
  

add_residuals(birthweight_data, fit_df) %>% 
  ggplot(aes(x = resid)) +
  geom_density()
  
```

## problem 1 model 2 and 3

model 2 using birth length and gestational age in weeks at predictors

```{r}
fit_df2 = lm(bwt ~ blength + gaweeks, data = birthweight_data)
summary(fit_df2)
```

model 3 using head circumference, length, sex and all interactions

```{r}
fit_df3 = lm(bwt ~ babysex + bhead + blength + babysex * bhead + babysex * blength + bhead * blength + babysex * bhead * blength, data = birthweight_data)
summary(fit_df3)
```

## problem 1 use CV to compare models

```{r}
cv_df_p1 = 
  crossv_mc(birthweight_data, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

fit models and extract RMSE

```{r}
cv_df1_RMSE =
  cv_df_p1 %>% 
  mutate(
    mod_df1 = map(.x = train, ~lm(bwt ~ fincome + ppbmi, data = .x)),
    mod_df2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_df3 = map(.x = train, ~lm(bwt ~ babysex + bhead + blength + babysex * bhead + babysex * blength + bhead * blength + babysex * bhead * blength, data = .x))
  ) %>% 
  mutate(
    rmse_df1 = map2_dbl(.x = mod_df1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_df2 = map2_dbl(.x = mod_df2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_df3 = map2_dbl(.x = mod_df3, .y = test, ~rmse(model = .x, data = .y))
  )
```

RMSE distribution

```{r}
cv_df1_RMSE %>% 
  select(.id, starts_with("rmse")) %>% 
    pivot_longer(
    rmse_df1:rmse_df3,
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_boxplot()
  
```


## Problem 2

load the dataset

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Let's try bootstrapping 

Part 1 identify the r squared CI

```{r}
weather_bootstrap_results =
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)
```

```{r}
weather_bootstrap_results %>% 
  janitor::clean_names() %>% 
  summarize(
    ci_lower = quantile(r_squared, 0.025),
    ci_upper = quantile(r_squared, 0.975)
  )
```

Part 2 log(β^0∗β^1) CI

```{r}
weather_bootstrap2_results =
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)
```



```{r}
weather_bootstrap2_results %>% 
  janitor::clean_names() %>% 
  select(term, estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>%
  janitor::clean_names() %>% 
  unnest(tmin) %>% 
  unnest(intercept) %>% 
  mutate(
    log_data = log(intercept*tmin)
  ) %>% 
  summarize(
    ci_lower = quantile(log_data, 0.025), 
    ci_upper = quantile(log_data, 0.975)
  )

  
```



























